Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-11 paper-ieee-trans.tex
Defining DevOps and rephrasing 3 pillars

In the following sections, we describe the three main pillars that sustain the project's strategy to attain reliability throughout the
% Comment
%%P3 C2 L29: This introductory paragraph goes into a bit too much jargony detail, I think, especially given that it is followed by in-depth coverage of each "pillar". I suggest a clearer identification of each pillar, maybe via bullets or definition paragraphs, avoiding or with general-audience definition of jargon like DevOps, delivery mechanisms, two-factor validation, pilot testbeds, and early adoption. I appreciate this may all be highly meaningful to someone steeped in this operational area, but to an interested outsider it reads much like management jargon -- particuarly the final sentence: is this a long-winded way of saying "used during the commissioning period"?
software lifecycle. A solid \textit{Software Quality Assurance (SQA) criteria
and metrics gathering definition} provides guidelines to develop quality
software, validating each change in the code, and facilitating its adoption. The software lifecycle is continuously monitored
by a set of metrics, allowing prompt reactions to detected malfunctions throughout the
process. A \textit{bottom--up adoption of DevOps principles} promotes automation to enable
the foregoing change--based development process and set up advanced delivery mechanisms.
The last key pillar is the \textit{two--factor validation} carried out over the project's pilot testbeds and
e--Infrastructure resource provider's early--adoption.

@@

\subsection{DevOps practices}
\label{sec:devops}
% Comment
%P5 C2 L21: Define DevOps!
The DevOps methods emphasize the SQA techniques to avoid infrastructure
disruption whenever new developments are deployed into production systems. The
following DevOps approaches have been progressively adopted throughout the project's
lifetime, being one of its major outcomes in terms of software reliability.

@@

>>>>

In the following sections, we describe the three main pillars that sustain the project's strategy to attain reliability throughout the
% Comment
%%P3 C2 L29: This introductory paragraph goes into a bit too much jargony detail, I think, especially given that it is followed by in-depth coverage of each "pillar". I suggest a clearer identification of each pillar, maybe via bullets or definition paragraphs, avoiding or with general-audience definition of jargon like DevOps, delivery mechanisms, two-factor validation, pilot testbeds, and early adoption. I appreciate this may all be highly meaningful to someone steeped in this operational area, but to an interested outsider it reads much like management jargon -- particuarly the final sentence: is this a long-winded way of saying "used during the commissioning period"?
software lifecycle:
\begin{enumerate}
    \item The definition of a \textit{Software Quality Assurance (SQA) criteria and a metrics gathering procedure} to provide guidelines
    aiming at developing quality software, validating each change in the code, to facilitate its adoption. The software lifecycle is
    continuously monitored by a set of metrics, allowing prompt reactions to detected malfunctions that may occur throughout the process. 
    \item The \textit{promotion of automation} to enable the foregoing change--based validation approach and to accelerate the delivery
    process of new software versions.
    \item A post-release validation to be carried out over the project's \textit{preview testbeds}, where the new product versions
    are deployed as part of the integration validation, and the \textit{testing in production environments} by external resource providers.
\end{enumerate}

@@

\subsection{Software quality validation and delivery automation}
\label{sec:devops}
% Comment
%P5 C2 L21: Define DevOps!
Tackling the granularity of the former SQA requirements -- most of which accounted in a per--change basis --
is hardly achieved without the aid of automation. The introduction of automation to validate the quality
requirements increases the overall reliability of the produced software: automated testing is more 
time-efficient, leading to higher coverages and increased defect detection, when compared with a manual
approach \cite{rafi2012}.

As any new change, involving a new feature or fix, passes through the automated
SQA machinery, the software is always ready to be released. As a result, the often compromised harmonization
between the continouous release of new features -- pushed by the development teams -- and the maintenance of
stable production systems -- demanded by users and resource providers -- can be guaranteed. The DevOps culture
theorizes and provides practical solutions that aim at unifying both software development (dev) and software
operations (ops) teams, by emphasizing the SQA techniques to avoid infrastructure disruption whenever new
developments are deployed into production systems. The following DevOps approaches have been progressively
adopted throughout the project's lifetime, being one of its major outcomes in terms of software reliability.

@@

\bibitem{rafi2012}
D. M. Rafi el al.,
Benefits and limitations of automated software testing: Systematic literature review and practitioner survey,
\emph{Proceedings of the 7th International Workshop on Automation of Software Test},
36--42, 2012.

\bibitem{chen2015}
L. Chen,
Continuous delivery: Huge benefits, but challenges too,
\emph{IEEE Software},
vol. 32, no 2, pp. 50--54, 2015.
